---
title: "Lab 1: Data Manipulation & Figures "
author: "Emily Lukshin"
output: html_document
---

### **A: Read in the "Badlands" dataset (either .csv or .txt)**

```{r}
  badlands <- read.csv("Badlands.csv")
```

### **B: What is the structure is your dataset and what class is each variable?**

```{r}
  str(badlands)
```

### **C: Provide a summary of your dataset.**

```{r}
  summary(badlands)
```

### **D: Provide the first 6 and last 6 observations of all variables.**

The first 6 observations:
```{r}
  head(badlands)
```

The last 6 observations:
```{r}
  tail(badlands, 6)
```

### **E: Create a subset of your data to include only *Native Forb*. Show a summary of the new subset.**

```{r}
  native_forbs <- subset(x = badlands, subset = Preferred.Lifeform == "Native Forb")

  summary(native_forbs)
```

### **F: Make a boxplot for each of the variables (as one figure).**

Preburn data:
```{r}
  library(tidyverse)
  ggplot(
   data = badlands,
   aes(
     x = Preferred.Lifeform,
     y = Pre_burn
   )
  ) +
   stat_boxplot(
    geom = "errorbar"
  ) +
  geom_boxplot(
  
  ) + 
  labs(
    x = "Preferred Lifeform",
    y = "Preburn",
    title = "Preburn"
  ) + 
  theme_classic( )
```

1 Year Post Burn data:
```{r}
  library(tidyverse)
  ggplot(
   data = badlands,
   aes(
     x = Preferred.Lifeform,
     y = X1yr_post_burn
   )
  ) +
   stat_boxplot(
    geom = "errorbar"
  ) +
  geom_boxplot(
  
  ) + 
  labs(
    x = "Preferred Lifeform",
    y = "1st Year After Burn",
    title = "1st Year After Burn"
  ) + 
  theme_classic( )
```

2 Years After Burn
```{r}
  library(tidyverse)
  ggplot(
   data = badlands,
   aes(
     x = Preferred.Lifeform,
     y = X2yr_post_burn
   )
  ) +
   stat_boxplot(
    geom = "errorbar"
  ) +
  geom_boxplot(
  
  ) + 
  labs(
    x = "Preferred Lifeform",
    y = "2nd Year Post Burn",
    title = "2nd Year After Burn"
  ) + 
  theme_classic( )
```
--- 
## The following must be answered to be graded: 

### **G: Since you worked in partners, briefly explain how you split the work between the two of you.** 

We worked through check part together and completed the assignment with the help of each other.

### **H: What did you struggle with most in this lab?**

I think the hardest part was remembering the function names and getting the syntax correct so that the code would run properly.


